Revisiting Child and Adolescent Depression Treatments

### 2024-05-10 Manuscript_for_rendering_in_word.qmd
new prisma

For adolescent depression, there are limited data from head-to-head trials of medication and psychotherapy, and hence recommendations must be derived from indirect comparisons of treatment efficacy. The UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2023]. This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021]. However, a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e. treatment A with treatment C, via studies that directly compare A with B and B with C) evidence, concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e. pill placebo) or psychotherapy controls. The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004]. Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?

@@

We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents. For the psychotherapy trials, we utilised open data from the previous meta-analysis (see [here](https://www.metapsy.org/)). For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves. We excluded three studies because they had no control arm. We were unable to locate and complete extraction for one RCT (Almeida-Montes et al., 2005). Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.

For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials. Two authors screened 450 titles and abstracts, and 38 full text records. Seven studies met inclusion criteria and one author completed data extraction for these papers. See @fig-prisma in the Supplement for PRISMA diagram.

@@

The data for the studies included in this meta-analysis are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].

@@

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-all
#| fig-cap: "Metanalytic estimates of within-group changes: all studies"
#| fig-cap-location: top

@@

Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`). Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.

@@

Overall, the active arms of psychotherapy studies were considerably more intensive than the control arms they were compared against (see @tbl-intensity-of-int for summary statistics). Active intervention arms featured significantly more sessions than control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`). These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`). The total hours involved in an intervention were higher in active vs control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the total period of the intervention was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).

@@

This paper took as its starting point the question of how anyone, be it a patient, parent, or clinician, should decide whether to opt for medication or psychotherapy for the treatment of adolescent depression. In order to address this question, we asked whether psychotherapy and medication are comparable on the basis of the existing evidence. Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two modalities. First, whether the participants of trials in one modality are comparable to those in another modality. Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.

Starting with the first question, we find evidence that participants in the two treatment modalities differ in the following key aspects: those enrolled in medication trials are more likely to be male and have more severe depression compared to those in psychotherapy trials. By contrast, there were no significant differences in age.

Severity is important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009]. Some studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however, these are within modality (e.g. within CBT studies), i.e. within those people who have chosen to be in the particular trial and modality. Moreover, there is evidence that severity may represent different subtypes in terms of course of depression and its outcomes in real life settings [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].

Similarly, we found that on average there were about 7% more females in psychotherapy trials. Whilst there is little evidence that sex moderates treatment response within modality in adult trials of depression [@cuijpersGENDERPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.

We then turned to our second basic question, about whether key conditions of the trial design were comparable between modalities. We find a series of critical differences between the two modalities.

First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs. Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in non-industry trials which are also more likely to show lower pill placebo efficacy. Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where primacy is given to the number of recruited participants which is the primary unit of reimbursement.

Second, psychotherapy controls have moderate effect size (-0.5) whereas pill-placebo has very large effect size (-1.9). Our analysis could be critiqued as it relies on comparing the within arm symptom change of each trial taken out of randomization, which is generally ill advised. This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving the randomization (in order to balance confounders) is critical. However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomization structure. More importantly, we do not make the claim with our analyses that these differences are genuinely due to efficacy differences; they may well be because of the fact that the people who attend psychotherapy and medication trials are different and therefore respond differently. In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences concerning the comparison of the two modalities. This is all the more so as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings. Our results make obvious that comparing treatments based on the effect sizes of each modality (relative to their respective control arms) is misleading.

Moving beyond comparison between the two modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving the treatment. An optimal control condition is one where the treatment differs but everything else is equal. An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind). Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the "all else is equal" assumption. Most (`r round(type_counts$wl_cau_percentage[1], 2)`%) of psychotherapy RCT control conditions are either waitlist or TAU, both of which are very likely to create negative expectations for participants not randomized to treatment. Thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting. But we also find that even psychological controls were unreasonable counterfactuals. In order to test that a psychological treatment is effective per se (e.g. because of the cognitive techniques the therapist deploys) rather than because of generic effects (e.g. pleasant human contact), aspects such as human contact time should be matched. We find that there are vast differences between treatment and control arms in psychotherapy trials which may lead to an inflation of the true efficacy of psychological treatments.

Given all of the above, the certainty with which guidelines recommend psychotherapy over medication for adolescent depression is surprising. Indeed, we believe that our findings have a number of profound implications for patients, their families, clinicians and policy makers and we list these below.

@@

Second, the low quality of control conditions of psychotherapy trials for adolescent depression should prompt a rethinking of what needs to be done to create fair comparators. Indeed, investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls. There are examples of psychotherapy RCTs where such rigor has been applied, such as @youngRandomizedDepressionPrevention2016 where active and control arms were matched on frequency and duration of sessions, as well as human contact with both therapists and group-members.

@@

In summary, our data give cause for consternation about the state of the evidence for treatments of youth depression, one of the most common and debilitating disorders in young people. Our data question the state of knowledge about the efficacy of psychotherapies and, in particular, the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people. Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choices than what currently exists.

@@

```{r, echo=FALSE}
#| label: fig-prisma
#| fig-cap: "PRISMA chart summarising the screening process for the systematic review"
#| fig-cap-location: top
knitr::include_graphics("PRISMA.png")
```

@@

Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016]. A dataset was made available online though did not include means or standard deviations at baseline or post-test. We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves. We excluded three studies because they had no control arm. We were unable to locate and therefore complete extraction for one RCT (Almeida-Montes et al., 2005). Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-no-wl
#| fig-cap: "Metanalytic estimates of within-group changes: waitlist studies excluded"
#| fig-cap-location: top
#| fig-title: Figure S

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-clin
#| fig-cap: "Metanalytic estimates of within-group changes: subclinical studies excluded"
#| fig-cap-location: top

@@

```
```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-cdrs
#| fig-cap: "Metanalytic estimates of within-group changes: CDRS studies only"
#| fig-cap-location: top

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-hamd
#| fig-cap: "Metanalytic estimates of within-group changes: HAM-D studies only"
#| fig-cap-location: top

>>>>

For adolescent depression, there are limited data from head-to-head trials of medication and psychotherapy, and hence recommendations must be derived from indirect comparisons of treatment efficacy. The UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2019]. This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021]. However, a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e. treatment A with treatment C, via studies that directly compare A with B and B with C) evidence, concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e. pill placebo) or psychotherapy controls. The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004]. Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?

@@

We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents. For the psychotherapy trials, we utilised open data from the previous meta-analysis (see [here](https://www.metapsy.org/)). For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves. We excluded three studies because they had no control arm. We were unable to locate and complete extraction for two RCTs (Almeida-Montes, 2005; Eli Lilly, 1986). Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.

For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials. Two authors screened 450 titles and abstracts, and 38 full text records. Seven studies met inclusion criteria and one author completed data extraction for these papers (see @fig-prisma for PRISMA diagram).

@@

The data for the studies included in this meta-analysis are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\]. Please see @fig-prisma for a summary of the systematic review and the sources of included RCTs.

@@

```{r, echo=FALSE}
#| label: fig-prisma
#| fig-cap: "PRISMA chart summarising sources of included studies"
#| fig-cap-location: top
knitr::include_graphics("PRISMA.png")
```

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-all
#| fig-cap: "Meta-analytic estimates of within-group changes: all studies"
#| fig-cap-location: top

@@

As shown in Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`). Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.

@@

As seen in @tbl-intensity-of-int active conditions featured significantly more sessions than control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`). These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`). The total intervention hours were higher in active vs control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the duration was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).

@@

This paper sought to address the question of whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence. Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two modalities. First, whether the participants of trials in one modality are comparable to those in another modality. Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.

Starting with the first question, we found that participants in medication trials are comparable on age but more likely to be male and have more severe depression compared to those in psychotherapy trials. These are indicators that different people enter medication and psychotherapy trials, thereby violating basic assumptions of comparability between trials for each modality.

Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009]. Other studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however, these are within modality (e.g. within CBT studies), i.e. within those people who have chosen to be in the particular trial and modality. Moreover, there is evidence that severity may represent different subtypes in terms of course of depression and its outcomes in real life settings [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].

We then turned to our second basic question, about whether key conditions of the trial design were comparable between modalities. We found a series of critical differences between the two modalities.

First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs. Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in non-industry trials which are also more likely to show lower pill placebo efficacy. Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.

Second, psychotherapy controls have moderate effect size (-0.5) whereas pill-placebo has very large effect size (-1.9). Our analysis could be critiqued as it relies on comparing within arm symptom change per trial, therefore effectively breaking randomization. This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving the randomization (in order to balance confounders) is critical. However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomization structure. More importantly, we do not make the claim with our analyses that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently. In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences concerning the comparison of the two modalities. This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings. Our results make obvious that comparing treatments based on the between-group effect sizes of each modality is misleading.

Moving beyond comparison between the two modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving the treatment. An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind). Yet, our results show that psychotherapy trials are unlikely to fulfill some other basic conditions of the "all else is equal" assumption of a counterfactual condition. In order to test that a psychological treatment is effective per se (e.g. because of the specific techniques) rather than because of generic effects (e.g. pleasant human contact), aspects such as therapist contact time should be matched. We find that there are vast differences between treatment and control arms in psychotherapy trials which may artificially inflate estimates of the efficacy of psychological treatments. Additionally, it is notable that most (67.24%) psychotherapy RCT control conditions are either WL or TAU, both of which are likely to be associated with disappointment bias, thereby further inflating estimates of efficacy of psychological treatments.

Given all of the above, the certainty with which guidelines recommend psychotherapy over medication for adolescent depression is surprising. Indeed, we believe that our findings have several profound implications for patients, their families, clinicians and policy makers.

@@

Second, the low quality of control conditions of psychotherapy trials for adolescent depression should prompt a rethinking of what needs to be done to create fair comparators. Indeed, investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls. There are examples of psychotherapy RCTs where such rigor has been applied, such as @youngRandomizedDepressionPrevention2016 where active and control arms were matched on frequency and duration of sessions, and total amount of contact.

@@

In summary, the current findings give cause for consternation about the state of the evidence for treatments of youth depression. Our data question the state of knowledge about the efficacy of psychotherapies and, in particular, the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people. Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choices.

@@

@@

Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016]. A dataset was made available online though did not include means or standard deviations at baseline or post-test. We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves. We excluded three studies because they had no control arm. We were unable to locate and therefore complete extraction for two RCTs (Almeida-Montes, 2005; Eli Lilly, 1986). Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-no-wl
#| fig-cap: "Meta-analytic estimates of within-group changes: waitlist studies excluded"
#| fig-cap-location: top
#| fig-title: Figure S

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-clin
#| fig-cap: "Meta-analytic estimates of within-group changes: subclinical studies excluded"
#| fig-cap-location: top

@@

```
```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-cdrs
#| fig-cap: "Meta-analytic estimates of within-group changes: CDRS studies only"
#| fig-cap-location: top

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: fig-plot-means-hamd
#| fig-cap: "Meta-analytic estimates of within-group changes: HAM-D studies only"
#| fig-cap-location: top
